Identifying Values to Express Emotions with a Non-Anthropomorphic Platform

### 2017-04-23 JournalIJSR/IJSR.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

\begin{abstract}
Social environments are intricate spaces where people behave in ways that are socially accepted. In a similar way, robots that interact with humans on daily bases are expected to develop certain behaviours to be socially accepted by people. This creates the necessity to make robots with high social presence that let humans to feel comfortable with their presence. The straightest way to fulfill is through imitation of humans' characteristics, such us body shape, behaviors and social characteristics. As a consequence many social robots have been built with anthropomorphic embodiment, which could include features to express emotions. Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that not required anthropomorphic shape due to the nature of the tasks that they have to perform. As a consequence,  features not related with anthropomorphic embodiment should be exploited to support robot acceptance. This paper presents an experiment made to understand humans' perception of emotion for angular and linear velocity, body orientation, and movement direction. Therefore, a non-anthropomorphic platform was used in the experiments to let participants to focus on the desired features. Moreover a Likert questionnaire was used to measure participants' perception for different treatments. The Krippendorff's alpha agreement was used to create a top 10 table for each of the emotions listed in the questionnaire. The obtained results suggest values that could guide the implementation of the considered emotions in social robots.
\keywords{Human-Robot Interaction \and Emotion Expression \and Experiment \and Non-anthropomorphic Platform \and Emotions Expression with Non-anthropomorphic Platform}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\section{Related Work}
\input{./Parts/Emotion_Projection}
\section{The System}
\label{sec:system}
\input{./Parts/Platform}
\section{Experimental Design}
\label{sec:experiment}
\input{./Parts/ExperimentDesign}
\section{Results}
\label{sec:result}
\input{./Parts/Results}
\section{Conclusions and Further Work}
\input{./Parts/Conclusion}
\bibliographystyle{spmpsci}
\bibliography{Bibliography,BibloNew,Biblography}

>>>>

\begin{abstract}
Social environments are intricate spaces where people behave in ways that are socially accepted. In a similar way, robots that interact with humans on a daily bases are expected to develop certain behaviours to be socially accepted by people. This creates the necessity to point out our attention on social presence of robots, to let humans feel comfortable with them. The straightest way to fulfill this is through imitation of humans' characteristics, such us body shape, behaviors and social characteristics. As a consequence many social robots have been built with anthropomorphic embodiment, which could include features to express emotions. Although anthropomorphic embodiment may support robot acceptance in interactive tasks, there are robots that not required anthropomorphic shape due to the nature of the tasks that they have to perform. As a consequence,  features not related with anthropomorphic embodiment should be exploited to support robot acceptance. This paper presents an experiment made to understand humans' perception of emotion given angular and linear velocity, body orientation, and movement direction. Therefore, a non-anthropomorphic platform was used in the experiments to let participants to focus on the desired features. Moreover a Likert questionnaire was used to measure participants' perception for different treatments. The Krippendorff's alpha agreement was used to create a top 10 table for each of the emotions listed in the questionnaire. The obtained results suggest values that could guide the implementation of the considered emotions in social robots.
\keywords{Human-Robot Interaction \and Emotion Expression \and Experiment \and Non-anthropomorphic Platform \and Emotions Expression with Non-anthropomorphic Platform}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\section{Emotional Models}
\input{./Parts/EmotionModels}
\section{Related Work}
\input{./Parts/Emotion_Projection}
\section{The System}
\label{sec:system}
\input{./Parts/Platform}
\section{Experimental Design}
\label{sec:experiment}
\input{./Parts/ExperimentDesign}
\section{Results}
\label{sec:result}
\input{./Parts/Results}
\section{Discussion}
\label{sec:discussion}
\input{./Parts/Discussion}
\section{Conclusions and Further Work}
\input{./Parts/Conclusion}
\bibliographystyle{spmpsci}
\bibliography{Bibliography,BibloNew,Biblography}

### 2017-04-23 JournalIJSR/Parts/Conclusion.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

The values obtained in this experiment could be used to express emotions in non-anthropomorphic platforms. It is still needed to cross validate the values and to determine what values from the top ten could more accurately express the desired emotion. It is important to mention that is not expected to have a 100\% of correct emotion recognition by the participants. As it has been observed in previous work in humans and robots, it is not possible to get a 100\% of correct recognition. This cross validation would help to reduce the number of feature combinations to the ones with higher possibility of identification. Moreover, additional experiments should be done to obtain analogous values for changes in shape and in different platform's size.

>>>>

The values obtained in this experiment could be used as a guide to express emotions in non-anthropomorphic platforms with similar features as the one used in the experiment. It is still needed to cross validate the values and to determine what values from the top ten could more accurately express the desired emotion. It is important to mention that is not expected to have a 100\% of correct emotion recognition by the participants. As it has been observed in previous work in humans and robots, it is not possible to obtain a 100\% of correct recognition due to diverse factors such as current emotional state of the observer. This cross validation would help to reduce the number of feature combinations to the ones with higher possibility of identification. Moreover, additional experiments should be done to obtain analogous values for changes in shape and in different platform's size. Moreover, it is still necessary to study the influence that plays the embodiment on the perception of emotions. This is going to be beneficial to validate this study but it would also generalize other works done on the same direction.

Even thought the number of works studying how to project emotions with robotic platforms is increasing, it is still required a framework that standardize the processes for the design of this endevours. This could is due the following four reasongs. First, there are a variety of emotion theories that could be used as a based to design the experiments or case studies. Hence, researchers must know who to use them correctly and how they are connected among them. For example, the model suggested by Izard~\cite{Izard2007} redefines the idea of basic emotions and make a connection with dimensional theories. Second, researcher are using different platforms to do their experiments, at time of writing, there is not a formal evidence that clarify the impact of the embodiment on the perception of emotions. This generates situations in which two works could not be comparable. Third, the use of actors to generate the movements are not reliable. Actors use diverse techniques to create believable representations of specific emotions. However, this does not ensure that all actor convey emotions in same way. Therefore, several records are done and the ones with the highest agreement are selected. This brings the technical question on how to interpret the significance of agreement obtained~\cite{Russell2003}. Fourth, there is not a generic format to present the finding and movements used. Each researcher is using diverse methodologies to present their findings, for example some uses Laban's theory~\cite{Sharma2013} while others present the postures~\cite{NAO2013}.

### 2017-04-23 JournalIJSR/Parts/Discussion.tex
Last version of the article. This version includes most of reviewers´ comments, such as new references, explanation of parts that were not well explained before.

A table with subjects' answers was generated for each treatment. Table~\ref{table:example_table} is an example of the generated tables.

\begin{table*}
\centering
\caption{Example of the table generated for each experience. This table corresponds to the experience with $ID=1$.}
\label{table:example_table}
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
	\rotatebox{90}{ \textbf{Sex}} & 
	\rotatebox{90}{ \textbf{Background}} & 
	\rotatebox{90}{ \textbf{Age}} & 
	\rotatebox{90}{ \textbf{Country of Origin}} & 
	\rotatebox{90}{ \textbf{Happy}} &
	\rotatebox{90}{ \textbf{Excited}} & 
	\rotatebox{90}{ \textbf{Tender}} & 
	\rotatebox{90}{ \textbf{Scared}} & 
	\rotatebox{90}{ \textbf{Angry}} & 
	\rotatebox{90}{ \textbf{Sad}} & 
	\rotatebox{90}{ \textbf{Other}} & 
	\rotatebox{90}{ \textbf{Explain}} \\ \hline
	Masculine & electronic engineering & 29 & Iran &  0 & 2 & 8 & 0 & 0 & 0 & 0 & \  \\ \hline
	Feminine & Computer science & 25 & Italy &  0 & 0 & 6 & 0 & 0 & 8 & 0 & \  \\ \hline
	Masculine & Computer science & 24 & Italy &  0 & 0 & 0 & 8 & 0 & 7 & 0 & \  \\ \hline
	Feminine & Pedagogical Science & 26 & Italy &  0 & 0 & 0 & 0 & 0 & 0 & 7 & Dubbioso \\ \hline
	Masculine & Computer science & 24 & Italy &  4 & 8 & 0 & 0 & 0 & 0 & 0 & \  \\ \hline
\multicolumn{12}{c}{}
\end{tabular}
\end{table*}

For each table, mean, standard deviation, and median were calculated. It was not possible to use ANOVA test over the data because the assumption of normality is not satisfied in the collected data. This was checked using the Shapiro-Wilk Test.
Additionally, a contingency table for each emotion was generated in each treatment, as it is depicted in Table~\ref{table:table_contingency}, where the intensity for the rest of emotions is calculated as their mean of their intensity, including the option ``other''. Therefore a total of seven tables for each treatment were created. For all these tables, Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was calculated, which is a reliability coefficient to measure the agreement among different participants. Unlike other coefficients (e.g., $Kappa$), $\alpha$ is a generalization of several known reliability indices, and it applies to any number of observers, any number of categories, any type of data, incomplete or missing data, large and small sample sizes.

This calculation was done using the R's package \textit{irr}. To improve contingency tables' interpretation, it was decided to just register emotions' alpha and intensity values greater than zero. The $\alpha$ for each treatment is shown in Figure~\ref{fig:alpha_experience}. As it could be observed, this table does not provide any information about the interpretation for each emotion. Therefore, it was decided to create top ten raking of treatments from the contingency tables of each emotion. This ranking is generated considering the following items in the respective order:(i) the mean intensity of the respective emotion, (ii) the alpha agreement of contingency table for the respective emotion, and (iii) the alpha agreement for the specific treatment. From the resulting tables~\ref{table:happy_top_ten},~\ref{table:Angry_top_ten},~\ref{table:Sad_top_ten}, and~\ref{table:Scared_top_ten}, it is possible to notice:

@@

	\item \textit{Anger} is highly perceived with an angle of $0.087$ (seven over ten) and with linear velocities over $200 mm/s$. It seems that people attribute anger to fast velocities, both angular and linear, small angle of oscillation and the robot facing the persons while approaching them. 
\end{itemize} 
%alpha general

\begin{figure*}
	\centering
	\includegraphics[width=1.0\textwidth]{./Images/Alpha.png} 
	\caption{Alpha values for each movement.}
	\label{fig:alpha_experience}
\end{figure*}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Happiness.  This tops table was generated by ordering the results from highest to lowest first by Happy mean, then by Happy alpha, and finally by Movement alpha.}
\label{table:happy_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &   
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	0 & 0 & 500 & 3 & 0.349 &  0.38 & 0.71 & 0 & 0 & 0 & 0.13 & 0 & 0.13 & 6.8 & 3 & 2.6 & 0 & 1.4 & 0 & 1.4 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 0 & 2 & 0.174 &  0.53 & 0.71 & 0 & 0 & 0 & 0 & 0 & 0 & 6.8 & 3.8 & 2 & 0 & 0 & 0 & 0 \\ \hline
	0 & 0 & 900 & 3 & 0.174 &  0.33 & 0.22 & 0 & 0.13 & 0 & 0 & 0 & 0 & 6.6 & 2.6 & 0.6 & 0 & 1.6 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 0 & 3 & 0.349 &   0.21 & 0.21 & 0 & 0.13 & 0 & 0.23 & 0.34 & 0 & 6.6 & 3.6 & 1.4 & 2 & 0.8 & 0.4 & 0 \\ \hline
	$\pi$ & 0 & 900 & 3 & 0.349 &   0.48 & 0.11 & 0.72 & 0.12 & 0 & 0.76 & 0 & 0 & 6.4 & 6.8 & 1.2 & 4 & 0.2 & 0 & 0 \\ \hline
	0 & $\pi$ & 0 & 2 & 0.349 &  0.34 & 0.71 & 0 & 0 & 0.13 & 0.47 & 0.23 & 0 & 6 & 1.4 & 3.2 & 1.6 & 0.4 & 0.6 & 0 \\ \hline
	$\pi$ & $\pi$ & 0 & 2 & 0.174 &   0.31 & 0.12 & 0 & 0 & 0.61 & 0 & 0 & 0.13 & 6 & 4.8 & 4.8 & 0.4 & 0 & 0 & 2 \\ \hline
	$\pi$ & 0 & 500 & 2 & 0.349 &  0.43 & 0.11 & 0 & 0 & 0 & 0.13 & 0 & 0 & 6 & 0 & 3.4 & 0 & 0.6 & 0 & 2 \\ \hline
	0 & 0 & 500 & 1 & 0.174 &  0.24 & 0.11 & 0 & 0 & 0 & 0 & 0 & 0.13 & 6 & 4 & 4.2 & 0 & 2.2 & 0 & 1.2 \\ \hline
	$\pi$ & 0 & 200 & 3 & 0.349 &  0.28 & 0.22 & 0 & 0 & 0 & 0 & 0 & 0 & 5.8 & 0.8 & 3 & 0 & 0 & 0 & 1.4 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Anger. This tops table was generated by ordering from highest to lowest first by Angry mean, then by Angry alpha, and finally by Movement alpha.}
\label{table:Angry_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &  
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	0 & 0 & 0 & 2 & 0.087 & 0.19 & 0 & 0.13 & 0.13 & 0.13 & 0.22 & 0 & 0 & 3.2 & 1.4 & 1.2 & 1.8 & 6.4 & 0 & 0 \\ \hline
	0 & 0 & 900 & 2 & 0.087 & 0.29 & 0.13 & 0 & 0.76 & 0.13 & 0.21 & 0 & 0 & 1.6 & 3.8 & 0.2 & 1 & 6.4 & 0 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 900 & 0 & 0 & 0.60 & 0 & 0 & 0 & 0.13 & 0.73 & 0 & 0 & 0 & 1.6 & 0 & 1.4 & 6.2 & 0 & 0 \\ \hline
	0 & 0 & 900 & 3 & 0.349 & 0.44 & 0 & 0 & 0 & 0 & 0.12 & 0 & 0 & 3 & 5 & 0 & 2.8 & 6.2 & 0 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 200 & 3 & 0.087 & 0.41 & 0 & 0 & 0 & 0 & 0.11 & 0.47 & 0 & 0 & 4.8 & 2.6 & 0 & 5.8 & 0.4 & 0 \\ \hline
	$\pi$ & 0 & 500 & 3 & 0.087 & 0.44 & 0.13 & 0 & 0 & 0 & 0.43 & 0 & 0 & 0.8 & 2.6 & 0 & 1.4 & 5.2 & 0 & 0 \\ \hline
	0 & 0 & 200 & 3 & 0.087 & 0.13 & 0.13 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 2.4 & 5.2 & 0 & 1.8 \\ \hline
	0 & 0 & 900 & 1 & 0.087 & 0.54 & 0 & 0.16 & 0 & 0 & 0.16 & 0 & 0 & 2.4 & 6.4 & 0 & 0 & 5 & 0 & 0 \\ \hline
	0 & 0 & 900 & 0 & 0 & 0 & 0.13 & 0 & 0.13 & 0.13 & 0 & 0 & 0.13 & 1.6 & 3 & 1 & 1.6 & 5 & 0 & 1.8 \\ \hline
	$\pi$ & 0 & 500 & 2 & 0.087 & 0.30 & 0.13 & 0 & 0 & 0 & 0.21 & 0 & 0 & 1 & 1.8 & 0 & 3.4 & 4.8 & 0 & 0 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Fear.  This tops table was generated by ordering from highest to lowest first by Fear mean, then by Fear alpha, and finally by Movement alpha.}
\label{table:Scared_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	$\pi$ & $\pi$ & 900 & 2 & 0.174 & 0.85 & 0 & 0 & 0.15 & 0.83 & 0 & 0 & 0 & 0 & 0 & 1.2 & 9.6 & 0 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 900 & 1 & 0.087  & 0.73 & 0 & 0 & 0.15 & 0.79 & 0 & 0.79 & 0 & 0 & 0 & 0.6 & 9.6 & 0 & 0.2 & 0 \\ \hline
	$\pi$ & $\pi$ & 500 & 3 & 0.087 & 0.41 & 0.13 & 0 & 0 & 0.75 & 0 & 0 & 0 & 2 & 3.4 & 0 & 9 & 3.6 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 500 & 2 & 0.174 & 0.33 & 0.24 & 0.24 & 0 & 0.34 & 0.24 & 0 & 0.25 & 1.33 & 1.5 & 0 & 7.83 & 0.66 & 0 & 1.66 \\ \hline
	$\pi$ & $\pi$ & 500 & 2 & 0.087 & 0.68 & 0 & 0 & 0 & 0.72 & 0.13 & 0 & 0 & 0 & 0 & 0 & 7.8 & 0.6 & 2.20 & 0 \\ \hline
	$\pi$ & $\pi$ & 200 & 2 & 0.087 & 0.44 & 0.13 & 0.13 & 0 & 0.66 & 0 & 0 & 0 & 1 & 1 & 1.2 & 7.6 & 1.6 & 0 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 0 & 2 & 0.087 & 0.35 & 0.35 & 0.13 & 0 & 0.22 & 0 & 0 & 0 & 0.4 & 1.2 & 0 & 7.4 & 3 & 0 & 0 \\ \hline
	0 & $\pi$ & 900 & 3 & 0.087 & 0.53 & 0 & 0 & 0 & 0.30 & 0 & 0 & 0 & 0 & 0 & 0 & 7 & 2.20 & 0 & 0 \\ \hline
	$\pi$ & $\pi$ & 500 & 3 & 0.349 & 0.20 & 0.13 & 0.13 & 0 & 0.16 & 0.34 & 0 & 0 & 1.8 & 1.6 & 0 & 6.8 & 0.4 & 2.4 & 0 \\ \hline
	$\pi$ & $\pi$ & 200 & 2 & 0.174 & 0.53 & 0 & 0 & 0.13 & 0.71 & 0.13 & 0.13 & 0 & 0 & 0 & 1 & 6.6 & 0.8 & 1.2 & 0 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\centering
\small
\caption{Top 10 attributions for Sadness.  This tops table was generated by ordering from highest to lowest first by Sadness mean, then by Sadness alpha, and finally by Movement alpha.}
\label{table:Sad_top_ten}
\rotatebox{-90}{
\begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |  }
\hline
\multicolumn{5}{|c|}{Features} & 
\multicolumn{8}{|c|}{Alpha} & 
\multicolumn{7}{c|}{Mean} \\ \hline
	\rotatebox{90}{\textbf{Direction (rad)}} &
	\rotatebox{90}{\textbf{Orientation (rad)}} & 
	\rotatebox{90}{\textbf{Linear V. (mm/sec)}} &
	\rotatebox{90}{\textbf{Angular V. (rad/sec)}} &
	\rotatebox{90}{\textbf{Angle (rad)}} &
	\rotatebox{90}{\textbf{General}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} & 
	\rotatebox{90}{\textbf{Happiness}} & 
	\rotatebox{90}{\textbf{Excitement}} & 
	\rotatebox{90}{\textbf{Tenderness}} & 
	\rotatebox{90}{\textbf{Fear}} & 
	\rotatebox{90}{\textbf{Anger}} & 
	\rotatebox{90}{\textbf{Sadness}} & 
	\rotatebox{90}{\textbf{Other}} \\ \hline
	$\pi$ & 0 & 200 & 1 & 0.349 & 0.64 & 0 & 0 & 0 & 0 & 0.13 & 0.73 & 0.13 & 0 & 0 & 0 & 0 & 1.2 & 7.4 & 1.6 \\ \hline
	0 & $\pi$ & 0 & 1 & 0.349 & 0.39 & 0 & 0 & 0.13 & 0 & 0 & 0.22 & 0 & 0 & 0 & 1.8 & 0 & 0 & 7.2 & 3.2 \\ \hline
	0 & 0 & 200 & 1 & 0.349 & 0.18 & 0.13 & 0 & 0 & 0 & 0.13 & 0.11 & 0 & 1.6 & 2 & 5.4 & 2.6 & 1.6 & 6 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 200 & 0 & 0 & 0.10 & 0.13 & 0.29 & 0 & 0 & 0 & 0 & 0 & 0.8 & 0.4 & 1.8 & 0 & 0 & 6 & 3.2 \\ \hline
	$\pi$ & $\pi$ & 200 & 1 & 0.349 & 0 & 0 & 0 & 0.13 & 0.13 & 0.14 & 0 & 0 & 0 & 0 & 0.6 & 1.4 & 1.2 & 6 & 2.4 \\ \hline
	0 & $\pi$ & 200 & 0 & 0 & 0.27 & 0.13 & 0 & 0 & 0 & 0 & 0.21 & 0 & 1.2 & 0 & 3.4 & 1.8 & 0 & 5.8 & 0 \\ \hline
	$-\frac{\pi}{2}$ & 0 & 0 & 1 & 0.087 & 0.14 & 0 & 0.13 & 0.13 & 0.13 & 0 & 0.21 & 0.13 & 0 & 2 & 2 & 1.2 & 0 & 5.8 & 1.6 \\ \hline
	0 & $\pi$ & 200 & 1 & 0.349 & 0.40 & 0 & 0.13 & 0 & 0 & 0 & 0.57 & 0.13 & 0 & 0.8 & 3 & 3 & 0 & 5.6 & 0.6 \\ \hline
	$\pi$ & $\pi$ & 200 & 0 & 0 & 0.32 & 0.69 & 0.69 & 0 & 0 & 0 & 0.16 & 0 & 0.2 & 0.2 & 1.2 & 3.2 & 0 & 5.4 & 0 \\ \hline
	0 & $\pi$ & 200 & 1 & 0.087 & 0.36 & 0 & 0 & 0 & 0 & 0 & 0.16 & 0 & 0 & 0 & 3.6 & 3.6 & 0 & 5.4 & 0 \\ \hline
\multicolumn{16}{c}{}
\end{tabular}
}
\end{table}

\begin{table}
\caption{Contingency table formula used for each emotion and experience. Where $k$ is the kth experience, $j$ is jth emotion for the kth experience, $n$ is the total number of participants, and $Value$ is the intensity given by a participant.}
\label{table:table_contingency}
\small
\begin{tabular}{|l|l|l|}
\hline
Participant & Desire Emotion & Other Emotions \\
\hline
$1$ & $Value_{k,j}^{1}$  & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{1})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
$2$ & $Value_{k,j}^{2}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
... & ... & ...\\
\hline
$n$ & $Value_{k,j}^{n}$ & $\frac{\sum_{i=1}^{i<=7 \wedge i \neq j}(Value_{k,i}^{2})}{\sum_{i=1}^{i<=6 \wedge i \neq j}(1)}$\\
\hline
\multicolumn{3}{c}{}
\end{tabular}
\end{table}

>>>>

From the resulting tables~\ref{table:happy_top_ten},~\ref{table:Angry_top_ten},~\ref{table:Sad_top_ten}, and~\ref{table:Scared_top_ten}, it is possible to notice:

@@

	\item \textit{Anger} is highly perceived with an angle of $0.087$ (seven over ten) and with linear velocities over $200 mm/s$. It seems that people attribute anger to fast velocities, both angular and linear, small angle of oscillation and the robot facing the persons while approaching them. 
\end{itemize} 
%alpha general
Although this information gives suggest some parameters that could be used to express the emotions studied, this suggestions are limited to the platform used on it. Hence, it is still necessary to study the influence that plays the embodiment on the perception of emotions. This is going to be beneficial to validate this study but it would also generalize other works done on the same direction.
